UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-13 main.tex
:pencil: Update metamaterial-based scatterers
:pencil: Update antenna-based scatterer

% \begin{section}{Scattering/Reflecting Principles}
\begin{section}{Scattering Principles}
	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure*}
	\begin{subsection}{Scatterer Categories}
		Scattering refers to a change of moving direction of particles after colliding with others.
		It often involves \emph{diffuse reflection} where an incident ray is redistributed at many angles.
		An electromagnetic wave is scattered when an obstruction is placed in its path.
		In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} to produce various reflection patterns \cite{Liang2022}.
		\begin{subsubsection}{Antenna-Based Scatterer}
			Antenna-based scatterers first receive the impinging signals, then reradiate some back to the space and absorb the remainder potentially for energy harvesting.
			According to \cite{Hansen1989}, the reradiated part can be decomposed into \emph{structural} component that consistently contributes to the environment multipath, and \emph{antenna} component that depends on the antenna-load impedance mismatch.
			The former is modelled within channel estimation while the latter can be controlled by load switching \cite{Boyer2014}.
			For antenna-based scatterers, the reflection coefficient at load state $m$ is%
			\footnote{It corresponds to a linear scatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
			\begin{equation}
				\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
				\label{eq:reflection_coefficient}
			\end{equation}
			where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
		\end{subsubsection}
		\begin{subsubsection}{Metamaterial-Based Scatterer}
			% The core concept of metamaterials is to produce materi- als by using artificially designed and fabricated structural units made of metallic or dielectric materials to achieve the desired properties and functionalities. These subwave- length structural units—the constituent artificial “atoms” and “molecules” of the metamaterial—can be tailored in shape and size.

@@

			Metamaterial consists of numerous sub-wavelength structural units made of metallic or dielectric materials.
			% The shape and size of each unit cell can be artificially altered for customized response to the electromagnetic field.
			% One can change the effective permittivity or permeability of the metamaterial by manipulating the lattice constant and inter-atomic interaction \cite{Zhou2021}.
			The properties of unit cells can be artificially tuned for unconventional effective permittivity $\epsilon$ and permeability $\mu$, bringing customizable response to the electromagnetic field \cite{Zhou2021}.
			Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
			This mainly applies a phase shift on the reflected wave because any propagation into the metamaterial would be evanescent.
			% It mainly applies a phase shift on the reflected wave, while any propagation into the metamaterial would be evanescent.
			% The reflection happens at the boundary between free space and metamaterial, which mainly applies a phase shift on the reflected wave.
			% There exists several methods to change the equivalent impedance of metamaterial unit, such as
			% applied voltage on
			% functional materials, such as graphene [73] and liquid crystals [74], [75]
			Depending on the type of metamaterial, its equivalent impedance can be controlled by voltage (for functional materials \cite{Singh2020} and tunable diodes \cite{Costa2021}) or architecture (for resonant elements \cite{Bialkowski2008}).
			For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at metamaterial state $m$ is
			\begin{equation}
				\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
			\end{equation}
			where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$, and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
		\end{subsubsection}
		% TODO discuss how BC, SR, RIS relates to both
	\end{subsection}

@@

	\begin{subsection}{BackCom/SR: Backscatter Modulation}
		% Backscatter sources encode self message by \emph{randomly changing reflection states.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding complex constellation point $c_m$ by \cite{Thomas2012a}
		Backscatter sources encode self message by \emph{random reflection states variation.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $0 \le \alpha \le 1$ is the amplitude reflect ratio that controls the harvest-scatter tradeoff at the direction of interest.
		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others

@@

	\begin{subsection}{RIS: Channel Reconfiguration}
		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		\gls{ris} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is overall amplitude reflect ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

@@

		% For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?

@@

		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and the node $k$-user backward channel as $h_{\mathrm{B},k}$. Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all UniScatters.
		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all UniScatter nodes.
		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
		Under perfect synchronization, the equivalent primary channel is a function of \emph{coded} backscatter symbols
		\begin{subequations}
			\label{eq:equivalent_channel}
			\begin{align}
				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k   \\
				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
			\end{align}
		\end{subequations}
		where $\alpha_k$ is the amplitude reflect ratio of UniScatter node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of node $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
		\end{equation}
		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector with average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
		% The equivalent channel for primary link is subject to backscatter uncertainty
		% The equivalent primary channel is a function of backscatter symbols  as
		% \begin{equation}
		% 	% \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
		% 	\boldsymbol{h}_{\mathrm{E}}^H(\boldsymbol{x}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}.
		% 	\label{eq:equivalent_channel}
		% \end{equation}

@@

\begin{section}{Simulation Results}
	% TODO add distribution to initializer to smooth curves?
	% TODO compare PGD and primary-MRT beamformers
	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node UniScatter-enabled network.
	We assume the distance between \gls{ap} and user is \qty{10}{\meter}, and $K=2$ UniScatter nodes are uniformly dropped within a disk centered at the user of radius \qty{1}{\meter}.
	% The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
	The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
	For direct, forward and backward links, we set the path loss exponents to \num{2.6}, \num{2.4} and \num{2}, and the Ricean factor to \num{5}, \num{5} and \num{10}, respectively.
	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
	% and the path loss exponents for direct, forward and backward links are \num{2.6}, \num{2.4} and \num{2}, respectively.
	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\qty{36}{\dBm}$.
	All nodes have amplitude reflect ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=4$ input states.
	% and we consider amplitude reflect ratio $\alpha=0.5$ and symbol period ratio $N=20$.
	% The user has a receive antenna gain of \qty{3}{\dBi} and average noise power
	The user is with average noise power $\sigma_v^2=\qty{70}{\dBm}$ and receive antenna gain \qty{3}{\dBi}.
	All rate regions are averaged over at least \num{1000} instances, where ``PSP'' and ``BSP'' means primary and backscatter symbol periods, respectively.
	We choose decision design by \gls{smawk} \cite{He2021} as reference, and select discretize boundaries uniformly over the \qty{95}{\percent} confidence region of edge hypotheses.
	The parameters remain fixed unless otherwise specified.

>>>>

% \begin{section}{Scattering/Reflecting Principles}
\begin{section}{Scattering Principles}
	\begin{figure*}[!t]
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			\label{fi:block_diagram}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			\label{fi:equivalent_circuit}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			\label{fi:scatter_model}
		\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\begin{subsection}{Scatterer Categories}
		Scattering refers to a change of moving direction of particles after colliding with others.
		It often involves \emph{diffuse reflection} where an incident ray is redistributed at many angles.
		An electromagnetic wave is scattered when an obstruction is placed in its propagation path.
		In \gls{rf} applications such as \gls{bc}, \gls{sr} and \gls{ris}, the scatterer often includes \emph{variable-load antenna} or \emph{programmable metamaterial} with various reflection patterns \cite{Liang2022}.
		\begin{subsubsection}{Antenna-Based Scatterer}
			A typical antenna-based scatterer consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
			It first receives the impinging signals, then reradiates some back to the space and dissipates the remainder.
			According to transmission line theory, the scatter-absorb tradeoff depends on the impedance matching of the load and the antenna.
			For passive scatterers without dedicated energy source, a majority of incident wave is harvested to support node operation and the reradiated part can be relatively weak \cite{Thomas2012a}.
			% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
			% To support the operation of on-chip components, the majority of incident wave is consumed for energy harvesting
			% According to \cite{Hansen1989}, the reradiated part can be decomposed into \emph{structural} component that consistently contributes to the environment multipath, and \emph{antenna} component that depends on the antenna-load impedance mismatch.
			At the receiver, the observed signal can be further decomposed into \emph{structural mode} and \emph{antenna mode} components \cite{Hansen1989}.
			The former consistently contributes to environment multipath and is modelled within channel estimation, while the latter depends on impedance mismatch and can be used for backscatter modulation \cite{Boyer2014} and/or channel reconfiguration \cite{Liang2022}.
			For antenna-based scatterers, the reflection coefficient at load state $m$ is%
			\footnote{It corresponds to a linear scatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
				\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
				\label{eq:reflection_coefficient}
			where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
			% Antenna-based scatterers are typically considered in \gls{bc} and \gls{sr} literatures, while some \gls{ris}
			% BC and SR typically antenna-based, RIS both
		\end{subsubsection}
		\begin{subsubsection}{Metamaterial-Based Scatterer}
			% The core concept of metamaterials is to produce materi- als by using artificially designed and fabricated structural units made of metallic or dielectric materials to achieve the desired properties and functionalities. These subwave- length structural units—the constituent artificial “atoms” and “molecules” of the metamaterial—can be tailored in shape and size.

@@

			% Metamaterial consists of numerous sub-wavelength structural units made of metallic or dielectric materials.
			A typical metamaterial-based scatterer consists of multiple material layers and a smart controller \cite{Wu2020}.
			The outer metamaterial layer involves numerous sub-wavelength structural units made of metallic or dielectric materials.
			% The shape and size of each unit cell can be artificially altered for customized response to the electromagnetic field.
			% One can change the effective permittivity or permeability of the metamaterial by manipulating the lattice constant and inter-atomic interaction \cite{Zhou2021}.
			The properties of unit cells can be artificially tuned for unconventional effective permittivity $\epsilon$ and permeability $\mu$, producing customizable response to the electromagnetic field \cite{Zhou2021}.
			Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
			This mainly applies a phase shift on the reflected wave and any propagation into the metamaterial would be evanescent.
			% It mainly applies a phase shift on the reflected wave, while any propagation into the metamaterial would be evanescent.
			% The reflection happens at the boundary between free space and metamaterial, which mainly applies a phase shift on the reflected wave.
			% There exists several methods to change the equivalent impedance of metamaterial unit, such as
			% applied voltage on
			% functional materials, such as graphene [73] and liquid crystals [74], [75]
			Depending on the type of metamaterial, its equivalent impedance can be controlled by voltage (for functional materials \cite{Singh2020} and tunable diodes \cite{Costa2021}) or architecture (for resonant elements \cite{Bialkowski2008}).
			For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at metamaterial state $m$ is
			\begin{equation}
				\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
			\end{equation}
			where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$ and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
		\end{subsubsection}
		% TODO discuss how BC, SR, RIS relates to both: BC and SR typically antenna-based, RIS both
	\end{subsection}

@@

	\begin{subsection}{BackCom/SR: Backscatter Modulation}
		% Backscatter sources encode self message by \emph{randomly changing reflection states.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding complex constellation point $c_m$ by \cite{Thomas2012a}
		Backscatter sources encode self message by \emph{random reflection states variation.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $0 \le \alpha \le 1$ is the amplitude scattering ratio that controls the harvest-scatter tradeoff at the direction of interest.
		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others

@@

	\begin{subsection}{RIS: Channel Reconfiguration}
		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		\gls{ris} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is overall amplitude scattering ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

@@

		% ? For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?

@@

		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and the node $k$-user backward channel as $h_{\mathrm{B},k}$. Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all UniScatters.
		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all UniScatter nodes.
		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
		Under perfect synchronization, the equivalent primary channel is a function of \emph{coded} backscatter symbols
		\begin{subequations}
			\label{eq:equivalent_channel}
			\begin{align}
				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k   \\
				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
			\end{align}
		\end{subequations}
		where $\alpha_k$ is the amplitude scattering ratio of UniScatter node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of node $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
		\end{equation}
		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector with average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
		% The equivalent channel for primary link is subject to backscatter uncertainty
		% The equivalent primary channel is a function of backscatter symbols  as
		% \begin{equation}
		% 	% \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
		% 	\boldsymbol{h}_{\mathrm{E}}^H(\boldsymbol{x}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}.
		% 	\label{eq:equivalent_channel}
		% \end{equation}

@@

\begin{section}{Simulation Results}
	% TODO add distribution to initializer to smooth curves?
	% TODO compare PGD and primary-MRT beamformers
	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node UniScatter-enabled network.
	We assume the distance between \gls{ap} and user is \qty{10}{\meter}, and $K=2$ UniScatter nodes are uniformly dropped within a disk centered at the user of radius \qty{1}{\meter}.
	% The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
	The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
	For direct, forward and backward links, we set the path loss exponents to \num{2.6}, \num{2.4} and \num{2}, and the Ricean factor to \num{5}, \num{5} and \num{10}, respectively.
	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
	% and the path loss exponents for direct, forward and backward links are \num{2.6}, \num{2.4} and \num{2}, respectively.
	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\qty{36}{\dBm}$.
	All nodes have amplitude scattering ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=4$ input states.
	% and we consider amplitude scattering ratio $\alpha=0.5$ and symbol period ratio $N=20$.
	% The user has a receive antenna gain of \qty{3}{\dBi} and average noise power
	The user is with average noise power $\sigma_v^2=\qty{70}{\dBm}$ and receive antenna gain \qty{3}{\dBi}.
	All rate regions are averaged over at least \num{1000} instances, where ``PSP'' and ``BSP'' means primary and backscatter symbol periods, respectively.
	We choose decision design by \gls{smawk} \cite{He2021} as reference, and select discretize boundaries uniformly over the \qty{95}{\percent} confidence region of edge hypotheses.
	The parameters remain fixed unless otherwise specified.
